---
title: Variation in coverage and uptake of antivirals and neutralising monoclonal antibodies by STP
output:
  html_document:
  theme: journal
github_document:
  keep_html: TRUE
---
  
```{css, echo=FALSE}
pre {
  max-height: 300px;
  overflow-y: auto;
}
pre[class] {
  max-height: 200px;
}
```

<style>
  body {
    text-align: justify;
     font-size: 11pt}
</style>

  
```{r setup, include=FALSE}
# Document settings ----
knitr::opts_chunk$set(echo = TRUE)

# Preliminaries ----

## Import libraries
library(tidyverse)
library(here)
library(glue)
library(gt)
library(gtsummary)
library(reshape2)
library(stringr)
library(scales)
library(kableExtra)
library(knitr)
library(ggplot2)
library(png)
library(readr)
library(htmltools)

## Import custom user functions
source(here("analysis", "lib", "custom_functions.R"))

## Output directory
output_dir_rmd <- here("output", "variation")
fs::dir_create(output_dir_rmd)

## Redaction threshold
threshold = 8

## Functions
quibble <- function(x, q = c(0.25, 0.5, 0.75)) {
  ## function that takes a vector and returns a tibble of its quantiles
  tibble("{{ x }}" := quantile(x, q), "{{ x }}_q" := q)
}

## Import data
data_processed <- read_rds(here::here("output", "data", "data_processed_clean.rds"))

data_stp_all <-  read_csv(here::here("analysis/lib/stp_dict_total.csv"))

data_stp_tpp <- read_csv(here::here("output", "data", "input_stp.csv.gz"),
                         col_types = cols_only(                      
                           patient_id = col_integer(),
                           stp = col_character())) %>%
  group_by(stp) %>%
  summarise(n_tpp = n())

## End date
end_date <- as.Date("2022-04-28")

## Remove patients no longer registered at time of treatment and format variables
data_processed_clean0 <- data_processed  %>%
  filter(elig_start >= as.Date("2021-12-11") & elig_start <= end_date) %>%
  filter(has_died == 0,
         registered_eligible == 1 | registered_treated == 1) %>%
  mutate(
    
    # Age groups
    ageband = cut(
      age,
      breaks = c(12, 30, 40, 50, 60, 70, 80, Inf),
      labels = c("12-29", "30-39", "40-49", "50-59", "60-69", "70-79", "80+"),
      right = FALSE),
    
    # Vaccination status
    vaccination_status = fct_case_when(
      vaccination_status == "Un-vaccinated" ~ "Un-vaccinated",
      vaccination_status == "Un-vaccinated (declined)" ~ "Un-vaccinated (declined)",
      vaccination_status== "One vaccination" ~ "One vaccination",
      vaccination_status == "Two vaccinations" ~ "Two vaccinations",
      vaccination_status == "Three or more vaccinations" ~ "Three or more vaccinations",
      #TRUE ~ "Unknown",
      TRUE ~ NA_character_
    )
    
  )

## STP population coverage in TPP
eligibility_stp <- data_processed_clean0 %>%
  select(stp, elig_start)  %>%
  group_by(stp) %>%
  tally()

treatment_stp <- data_processed_clean0 %>%
  filter(!is.na(treatment_type)) %>%
  select(stp)  %>%
  group_by(stp) %>%
  tally() 

data_stp <- left_join(data_stp_all, data_stp_tpp, by = c("stp_id" = "stp")) %>%
  mutate(#n_tpp = round(n_tpp/7, digits = 0)*7,
         #total_list_size = round(total_list_size/7, digits = 0)*7,
         perc = round(n_tpp/total_list_size*100, digits = 0)) %>%
  left_join(eligibility_stp, by = c("stp_id" = "stp")) %>%
  left_join(treatment_stp, by = c("stp_id" = "stp")) %>%
  mutate(prop = round(n.y/n.x*100, digits = 0 )) 

stp_exclude <- data_stp %>%
  filter(perc < 10) %>%
  select(stp_id)

data_stp_clean <- data_stp %>%
  select(name, n_tpp, total_list_size, perc, n.y, n.x, prop)
colnames(data_stp_clean) <- c("STP", "Number of patients in TPP", "Total population", "Percentage of population included in TPP (%)",
                        "Number of treated patients in TPP", "Number of eligible patients in TPP", "Percentage treated (%)")

write_csv(data_stp_clean, fs::path(output_dir_rmd, "table_stp_coverage.csv"))

## Exclude STPs with <10% coverage
data_processed_clean <- data_processed_clean0 %>%
  filter(!(stp %in% stp_exclude$stp_id))
```

<br>

This report describes the coverage and uptake of antivirals and neutralising monoclonal antibodies for the treatment of non-hospitalised patients with COVID-19 by STP. Note, that a) practice-STP mappings used to calculate the coverage are as of March 2020 and since then some borders and population sizes may have changed and b) the subset of the population covered by TPP in each STP may not be representative of the whole STP and c) STPs with less than 10% population coverage in TPP practices have been omitted.

### Overall coverage of COVID-19 treatment, by STP decile

Between **`r format(min(data_processed_clean0$elig_start, na.rm = T), format = "%d-%b-%Y")`** and **`r format(max(data_processed_clean0$elig_start, na.rm = T), format = "%d-%b-%Y")`**, a total of `r format(plyr::round_any(data_processed_clean0 %>% nrow(), 10), big.mark = ",", scientific = FALSE)` non-hospitalised patients registered at a TPP practice in England were identified as potentially being eligible for receiving an antiviral or nMAB for treating COVID-19. Of these `r format(plyr::round_any(data_processed_clean0 %>% nrow(), 10), big.mark = ",", scientific = FALSE)` potentially eligible patients, `r format(plyr::round_any(data_processed_clean0 %>% filter(!is.na(treatment_date)) %>% nrow(), 10), big.mark = ",", scientific = FALSE)` (**`r round(plyr::round_any(data_processed_clean0 %>% filter(!is.na(treatment_date)) %>% nrow(), 10)/plyr::round_any(data_processed_clean0 %>% nrow(), 10)*100, digits = 0)`%**) received treatment from a CMDU. 

STP (used as a proxy for CMDU) was available for `r format(plyr::round_any(data_processed_clean %>% filter(!is.na(stp)) %>% nrow(), 10), big.mark = ",", scientific = FALSE)` (`r round(round(data_processed_clean %>% filter(!is.na(stp)) %>% nrow(), 10)/plyr::round_any(data_processed_clean0 %>% nrow(), 10)*100, digits = 0)`%) of eligible patients and `r format(plyr::round_any(data_processed_clean %>% filter(!is.na(stp), !is.na(treatment_date)) %>% nrow(), 10), big.mark = ",", scientific = FALSE)` (`r round(round(data_processed_clean %>% filter(!is.na(stp), !is.na(treatment_date)) %>% nrow(), 10)/plyr::round_any(data_processed_clean0 %>% filter(!is.na(treatment_date)) %>% nrow(), 10)*100, digits = 0)`%) of treated patients with a total of `r format(length(unique(data_processed$stp)), big.mark = ",", scientific = FALSE)` STPs identified. Of these `r format(length(unique(data_processed$stp)), big.mark = ",", scientific = FALSE)` STPs,  `r format(data_stp %>% filter(perc < 10) %>% nrow(), big.mark = ",", scientific = FALSE)` were excluded due to having less than 10% population coverage in TPP practices; `r format(sum(subset(data_stp, perc < 10)$n.x, na.rm = T), big.mark = ",", scientific = FALSE)` eligible patients and `r format(sum(subset(data_stp, perc < 10)$n.y, na.rm = T), big.mark = ",", scientific = FALSE)` treated patients.

```{r, coverage plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis' , fig.width=10, out.width = '100%', fig.cap = "**Figure 1 Cumulative total of potentially eligible patients for receiving an antiviral or nMABs for treating COVID-19 since 11th December 2021, stratified by STP decile.** Patients are considered eligible on the date of their positive SARS-CoV-2 test. Note, the overall number in each group is likely to be an overestimation due to including SARS-CoV-2 infection confirmed by either lateral flow or PCR test (where only PCR-confirmed infections should have been treated according to guidance in effect prior to 10th February 2022), and potentially including non-symptomatic patients. Decile values relating to patient counts of 0-7 have been redacted.", fig.topcaption=TRUE}

# Cumulative total of eligible patients by STP decile
eligible_stp_decile_n <- data_processed_clean %>%
  select(stp, elig_start)  %>%
  group_by(stp, elig_start) %>%
  tally() %>%
  arrange(stp, elig_start) %>%
  complete(elig_start = seq.Date(min(elig_start, na.rm = T), max(elig_start, na.rm = T), by="day"))  %>%
  mutate(count = ifelse(is.na(n), 0, n),
         cum_count = cumsum(count)) %>%
  select(-n) %>%
  group_by(elig_start) %>%
  mutate(cum_count_q = ntile(cum_count,10)/10) %>%
  ungroup() %>%
  select(decile = cum_count_q, elig_start, count, cum_count, stp) %>%
  arrange(decile, elig_start) %>%
  group_by(decile, elig_start) %>%
  summarise(n_patients = sum(cum_count, na.rm = T),
            n_stp = n_distinct(stp))

eligible_stp_decile <- data_processed_clean %>%
  select(stp, elig_start)  %>%
  group_by(stp, elig_start) %>%
  tally() %>%
  arrange(stp, elig_start) %>%
  complete(elig_start = seq.Date(min(elig_start, na.rm = T), max(elig_start, na.rm = T), by="day"))  %>%
  mutate(count = ifelse(is.na(n), 0, n),
         cum_count = cumsum(count),
         cum_count_rounded = plyr::round_any(cum_count, 5)) %>%
  select(-n) %>%
  group_by(elig_start) %>%
    summarise(quibble(cum_count, seq(0.1,0.9,0.1)),
              quibble(cum_count_rounded, seq(0.1,0.9,0.1))) %>%
  arrange(cum_count_q, elig_start) %>%
  filter(elig_start < end_date) %>%
  rename(decile = cum_count_q) %>%
  left_join(eligible_stp_decile_n, by = c("elig_start", "decile")) %>%
  mutate(cum_count_decile_redacted = ifelse(cum_count < 8, NA, cum_count_rounded)) %>%
  select(decile, elig_start, n_stp, n_patients, cum_count_decile = cum_count, cum_count_decile_redacted)

write_csv(eligible_stp_decile, fs::path(output_dir_rmd, "figure_1.csv"))
write_csv(eligible_stp_decile %>% 
            select(decile, elig_start, cum_count_decile_redacted) %>%
            filter(elig_start >= as.Date("2021-12-11") & elig_start <= as.Date("2022-04-28")), 
          fs::path(output_dir_rmd, "figure_1_redacted.csv"))

eligible_stp_decile <- eligible_stp_decile %>%
  mutate(line = ifelse(decile == "0.5", "Median", "Decile"))
  
eligible_stp_decile %>%
  filter(elig_start >= as.Date("2021-12-11") & elig_start <= as.Date("2022-04-28")) %>%
  ggplot(aes(x = elig_start, y = cum_count_decile_redacted, group = decile)) +
  geom_step(aes(colour = line, linetype = line)) +
  scale_color_manual(values = c("Decile" = "blue", "Median" = "blue")) +
  scale_linetype_manual(values = c("Decile" = "dashed", "Median" = "solid")) +
  theme_classic(base_size = 8) +
  scale_x_date(date_breaks = "2 week", date_labels =  "%d %b %Y") +
  labs(
    x = "Positive SARS-CoV-2 test date",
    y = "Number of patients eligible for receiving treatment",
    title = "")  +
  theme(legend.position = "bottom", 
        legend.title = element_blank()) +
  theme(
    axis.text = element_text(size = 10),
    axis.text.x = element_text(angle = 60, hjust = 1),
    axis.title = element_text(size = 10),
    axis.line.x = element_line(colour = "black"),
    panel.grid.minor.x = element_blank()) + 
  scale_y_continuous(labels = comma)

```

<br>

```{r, elig treatment type plot, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=10, out.width = '100%', fig.cap = "**Figure 2 Cumulative total of patients who received an antiviral or nMAB for treating COVID-19 since 16th December 2021, stratified by STP decile. Decile values relating to patient counts of 0-7 have been redacted.**", fig.topcaption=TRUE}

# Cumulative total of treated patients by stp decile
treated_stp_decile_n <- data_processed_clean %>%
  select(stp, treatment_date)  %>%
  group_by(stp, treatment_date) %>%
  tally() %>%
  arrange(stp, treatment_date) %>%
  complete(treatment_date = seq.Date(min(treatment_date, na.rm = T), max(treatment_date, na.rm = T), by="day"))  %>%
  mutate(count = ifelse(is.na(n), 0, n),
         cum_count = cumsum(count)) %>%
  select(-n) %>%
  group_by(treatment_date) %>%
  mutate(cum_count_q = ntile(cum_count,10)/10) %>%
  ungroup() %>%
  select(decile = cum_count_q, treatment_date, count, cum_count, stp) %>%
  arrange(decile, treatment_date) %>%
  group_by(decile, treatment_date) %>%
  summarise(n_patients = sum(cum_count, na.rm = T),
            n_stp = n_distinct(stp))

treated_stp_decile <- data_processed_clean %>%
  select(stp, treatment_date)  %>%
  group_by(stp, treatment_date) %>%
  tally() %>%
  arrange(stp, treatment_date) %>%
  complete(treatment_date = seq.Date(min(treatment_date, na.rm = T), max(treatment_date, na.rm = T), by="day"))  %>%
  mutate(count = ifelse(is.na(n), 0, n),
         cum_count = cumsum(count),
         cum_count_rounded = plyr::round_any(cum_count, 5)) %>%
  select(-n) %>%
  group_by(treatment_date) %>%
    summarise(quibble(cum_count, seq(0.1,0.9,0.1)),
              quibble(cum_count_rounded, seq(0.1,0.9,0.1))) %>%
  arrange(cum_count_q, treatment_date) %>%
  filter(treatment_date < end_date) %>%
  rename(decile = cum_count_q) %>%
  left_join(treated_stp_decile_n, by = c("treatment_date", "decile")) %>%
  mutate(cum_count_decile_redacted = ifelse(cum_count < 8, NA, cum_count_rounded)) %>%
  select(decile, treatment_date, n_stp, n_patients, cum_count_decile = cum_count, cum_count_decile_redacted)

write_csv(treated_stp_decile, fs::path(output_dir_rmd, "figure_2.csv"))
write_csv(treated_stp_decile %>% 
            select(decile, treatment_date, cum_count_decile_redacted) %>%
            filter(treatment_date >= as.Date("2021-12-11") & treatment_date <= as.Date("2022-04-28")), 
          fs::path(output_dir_rmd, "figure_2_redacted.csv"))

treated_stp_decile <- treated_stp_decile %>%
  mutate(line = ifelse(decile == "0.5", "Median", "Decile"))
  
treated_stp_decile %>%
  filter(treatment_date >= as.Date("2021-12-11") & treatment_date <= as.Date("2022-04-28")) %>%
  ggplot(aes(x = treatment_date, y = cum_count_decile_redacted, group = decile)) +
  geom_step(aes(colour = line, linetype = line)) +
  scale_color_manual(values = c("Decile" = "blue", "Median" = "blue")) +
  scale_linetype_manual(values = c("Decile" = "dashed", "Median" = "solid")) +
  theme_classic(base_size = 8) +
  scale_x_date(date_breaks = "2 week", date_labels =  "%d %b %Y") +
  labs(
    x = "Positive SARS-CoV-2 test date",
    y = "Number of patients receiving treatment",
    title = "(b)")  +
  theme(legend.position = "bottom", 
        legend.title = element_blank()) +
  theme(
    axis.text = element_text(size = 10),
    axis.text.x = element_text(angle = 60, hjust = 1),
    axis.title = element_text(size = 10),
    axis.line.x = element_line(colour = "black"),
    panel.grid.minor.x = element_blank()) + 
  scale_y_continuous(labels = comma)

```

<br>

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=10, out.width = '100%', fig.cap = "**Figure 3 Weekly proportion of eligible patients receiving an antiviral or nMAB for treating COVID-19 since 11th December 2021, stratified by STP decile.**", fig.topcaption=TRUE}

# Proportion of treated patients by stp decile
proportion_stp_decile_n_stp <- data_processed_clean %>%
  mutate(week = cut(elig_start + 2 , "week"),
         elig = 1, treat = ifelse(!is.na(treatment_date), 1, 0)) %>%
  select(stp, week, elig, treat) %>%
  group_by(stp, week) %>%  
  summarise(elig = sum(elig, na.rm = T),
            treat = sum(treat, na.rm = T)) %>%
  mutate(elig = ifelse(is.na(elig), 0, elig),
         treat = ifelse(is.na(treat), 0, treat)) %>%
  ungroup() %>%
  mutate(prop = treat/elig,
         week = as.Date(week) - 2) %>%
  mutate(prop_q = ntile(prop,10)/10) %>%
  group_by(prop_q, week) %>%
  summarise(n_stp = n_distinct(stp),
            n_elig = sum(elig, na.rm = T),
            n_treat = sum(treat, na.rm = T))

proportion_stp_decile <- data_processed_clean %>%
  mutate(week = cut(elig_start + 2 , "week"),
         elig = 1, treat = ifelse(!is.na(treatment_date), 1, 0)) %>%
  select(stp, week, elig, treat) %>%
  group_by(stp, week) %>%  
  summarise(elig = sum(elig, na.rm = T),
            treat = sum(treat, na.rm = T)) %>%
  mutate(elig = ifelse(is.na(elig), 0, elig),
         treat = ifelse(is.na(treat), 0, treat)) %>%
  ungroup() %>%
  mutate(prop = treat/elig,
         week = as.Date(week) - 2) %>%
  mutate(prop_q = ntile(prop,10)) %>%
  group_by(week) %>%
  summarise(quantile = scales::percent(c(seq(0.1,0.9,0.1))),
            prop = quantile(prop, c(seq(0.1,0.9,0.1))))  %>%
  mutate(decile = as.numeric(gsub("%", "", quantile))/100) %>%
  left_join(proportion_stp_decile_n_stp, by = c("decile" = "prop_q", "week" = "week")) %>%
  select(decile, week, n_stp, n_elig, n_treat, prop_decile = prop) %>%
  arrange(decile, week)

write_csv(proportion_stp_decile, fs::path(output_dir_rmd, "figure_3_counts.csv"))
write_csv(proportion_stp_decile %>%
            filter(week >= as.Date("2021-12-11") & week <= as.Date("2022-04-28")) %>% 
            select(decile, week, prop_decile),
          fs::path(output_dir_rmd, "figure_3.csv"))

proportion_stp_decile <- proportion_stp_decile %>%
  mutate(line = ifelse(decile == "0.5", "Median", "Decile"))
  
proportion_stp_decile %>%
  filter(week >= as.Date("2021-12-11") & week <= as.Date("2022-04-28")) %>%
  ggplot(aes(x = week, y = prop_decile, group = decile)) +
  geom_line(aes(colour = line, linetype = line)) +
  scale_color_manual(values = c("Decile" = "blue", "Median" = "blue")) +
  scale_linetype_manual(values = c("Decile" = "dashed", "Median" = "solid")) +
  theme_classic(base_size = 8) +
  scale_x_date(date_breaks = "2 week", date_labels =  "%d %b %Y") +
  labs(
    x = "Week",
    y = "Proportion of eligible patients who received treatment",
    title = "(b)")  +
  theme(legend.position = "bottom", 
        legend.title = element_blank()) +
  theme(
    axis.text = element_text(size = 10),
    axis.text.x = element_text(angle = 60, hjust = 1),
    axis.title = element_text(size = 10),
    axis.line.x = element_line(colour = "black"),
    panel.grid.minor.x = element_blank()) + 
  scale_y_continuous(labels = comma)

```


**Table 1 Count and proportion of potentially eligible patients in OpenSAFELY-TPP who have received treatment for COVID-19 since 16th December 2021, broken down by STP decile and treatment type.** Counts <8 have been redacted and counts >7 are rounded to the nearest 10; as a result percentages may not add up to 100%."

```{r, echo=FALSE, message=FALSE, warning=FALSE, results='asis', fig.width=10, out.width = '100%'}

# Eligible and treated table
stp_prop_deciles_lkup <- data_stp %>%
  filter(!is.na(prop)) %>% 
  mutate(prop = n.y/n.x*100,
         decile = ntile(prop, 9)/10,
         decile = as.numeric(as.character(decile))) %>%
  select(stp = stp_id, decile)

eligibility_table <- data_processed_clean %>%
  select(stp, elig_start)  %>%
  group_by(stp) %>%
  tally()

treatment_table <- data_processed_clean %>%
  filter(!is.na(treatment_type)) %>%
  select(stp, treatment_type)  %>%
  group_by(stp, treatment_type) %>%
  tally()  %>%
  group_by(treatment_type) %>%
  pivot_wider(
    id_cols = stp,
    names_from = treatment_type,
    values_from = n) %>%
  mutate(Casirivimab = ifelse(is.na(Casirivimab), 0, Casirivimab),
         Molnupiravir = ifelse(is.na(Molnupiravir), 0, Molnupiravir),
         Paxlovid = ifelse(is.na(Paxlovid), 0, Paxlovid),
         Remdesivir = ifelse(is.na(Remdesivir), 0, Remdesivir),
         Sotrovimab = ifelse(is.na(Sotrovimab), 0, Sotrovimab))

table_elig_treat <- left_join(eligibility_table, treatment_table, by = "stp") %>%
  mutate(Treated = Casirivimab + Molnupiravir + Sotrovimab + Paxlovid + Remdesivir) %>%
  select(stp, Eligibile = n, Treated, Paxlovid, Sotrovimab, Remdesivir, Molnupiravir, Casirivimab) %>%
  right_join(stp_prop_deciles_lkup, by = "stp") %>%
  group_by(decile) %>%
  summarise(Eligibile = sum(Eligibile, na.rm = T),
            Treated = sum(Treated, na.rm = T),
            Paxlovid = sum(Paxlovid, na.rm = T),
            Sotrovimab = sum(Sotrovimab, na.rm = T),
            Remdesivir = sum(Remdesivir, na.rm = T),
            Molnupiravir = sum(Molnupiravir, na.rm = T),
            Casirivimab = sum(Casirivimab, na.rm = T)) %>%
  left_join(data_stp %>%
              filter(!is.na(prop)) %>% 
              mutate(lci = round((n.y/n.x - 1.96*sqrt((n.y/n.x)*(1-n.y/n.x)/n.x))*100, digits = 0),
                     uci = round((n.y/n.x + 1.96*sqrt((n.y/n.x)*(1-n.y/n.x)/n.x))*100, digits = 0)) %>%
              summarise(quibble(prop, seq(0.1,0.9,0.1)),
                        quibble(lci, seq(0.1,0.9,0.1)),
                        quibble(uci, seq(0.1,0.9,0.1))) %>%
              mutate(prop = round(prop, digits = 0),
                     lci = round(lci, digits = 0),
                     uci = round(uci, digits = 0),
                     prop_q = as.numeric(as.character(prop_q))) %>%
              mutate(decile_value = paste(prop, " (", lci, "-", uci,  ")", sep = "")) %>%
              select(decile = prop_q,  decile_value), by = "decile") %>%
  select(decile, Eligibile, Treated, decile_value, Paxlovid, Sotrovimab, Remdesivir, Molnupiravir, Casirivimab) 

table_elig_treat_redacted <- table_elig_treat %>%
  mutate(
    # Redact values < 8
    Eligibile = ifelse(Eligibile < threshold, NA, as.numeric(Eligibile)),
    Treated = ifelse(Treated < threshold, NA, as.numeric(Treated)),
    Paxlovid = ifelse(Paxlovid < threshold, NA, as.numeric(Paxlovid)),
    Sotrovimab = ifelse(Sotrovimab < threshold, NA, as.numeric(Sotrovimab)),
    Remdesivir = ifelse(Remdesivir < threshold, NA, as.numeric(Remdesivir)),
    Molnupiravir = ifelse(Molnupiravir < threshold, NA, as.numeric(Molnupiravir)),
    Casirivimab = ifelse(Casirivimab < threshold, NA, as.numeric(Casirivimab)),
    # Round to nearest 10
    Eligibile = plyr::round_any(Eligibile, 10),
    Treated = plyr::round_any(Treated, 10),
    Paxlovid = plyr::round_any(as.numeric(Paxlovid), 10),
    Sotrovimab = plyr::round_any(as.numeric(Sotrovimab), 10),
    Remdesivir = plyr::round_any(as.numeric(Remdesivir), 10),
    Molnupiravir = plyr::round_any(Molnupiravir, 10),
    Casirivimab = plyr::round_any(Casirivimab, 10)) %>%
  arrange(desc(decile)) %>%
  mutate(Paxlovid_perc = paste(round(Paxlovid/Treated*100, digits = 0), " (",
                               round((Paxlovid/Treated - 1.96*sqrt((Paxlovid/Treated)*(1-Paxlovid/Treated)/Treated))*100, digits = 0),
                               "-",
                               round((Paxlovid/Treated + 1.96*sqrt((Paxlovid/Treated)*(1-Paxlovid/Treated)/Treated))*100, digits = 0), 
                               ")",
                               sep = ""),
         Sotrovimab_perc = paste(round(Sotrovimab/Treated*100, digits = 0), " (",
                                 round((Sotrovimab/Treated - 1.96*sqrt((Sotrovimab/Treated)*(1-Sotrovimab/Treated)/Treated))*100, 
                                       digits = 0),
                                 "-",
                                 round((Sotrovimab/Treated + 1.96*sqrt((Sotrovimab/Treated)*(1-Sotrovimab/Treated)/Treated))*100, 
                                       digits = 0), 
                                 ")",
                                 sep = ""),
         Remdesivir_perc = paste(round(Remdesivir/Treated*100, digits = 0), " (",
                                 round((Remdesivir/Treated - 1.96*sqrt((Remdesivir/Treated)*(1-Remdesivir/Treated)/Treated))*100, 
                                       digits = 0),
                                 "-",
                                 round((Remdesivir/Treated + 1.96*sqrt((Remdesivir/Treated)*(1-Remdesivir/Treated)/Treated))*100, 
                                       digits = 0), 
                                 ")",
                                 sep = ""),
         Molnupiravir_perc = paste(round(Molnupiravir/Treated*100, digits = 0), " (",
                                   round((Molnupiravir/Treated - 1.96*sqrt((Molnupiravir/Treated)*(1-Molnupiravir/Treated)/Treated))*100,
                                         digits = 0),
                                   "-",
                                   round((Molnupiravir/Treated + 1.96*sqrt((Molnupiravir/Treated)*(1-Molnupiravir/Treated)/Treated))*100, 
                                         digits = 0), 
                                   ")",
                                   sep = ""),
         Casirivimab_perc = paste(round(Casirivimab/Treated*100, digits = 0), " (",
                                  round((Casirivimab/Treated - 1.96*sqrt((Casirivimab/Treated)*(1-Casirivimab/Treated)/Treated))*100, 
                                        digits = 0),
                                  "-",
                                  round((Casirivimab/Treated + 1.96*sqrt((Casirivimab/Treated)*(1-Casirivimab/Treated)/Treated))*100, 
                                        digits = 0), 
                                  ")",
                                  sep = "")) %>%
  select(decile, Eligibile, Treated, decile_value, Paxlovid, Paxlovid_perc, Sotrovimab, Sotrovimab_perc, Remdesivir, 
         Remdesivir_perc, Molnupiravir, Molnupiravir_perc, Casirivimab, Casirivimab_perc) %>%  
  mutate(Paxlovid = ifelse(is.na(Paxlovid), "<8", Paxlovid),
         Paxlovid_perc = ifelse(Paxlovid_perc == "NA (NA-NA)", "--", Paxlovid_perc),
         Remdesivir = ifelse(is.na(Remdesivir), "<8", Remdesivir),
         Remdesivir_perc = ifelse(Remdesivir_perc == "NA (NA-NA)", "--", Remdesivir_perc),
         Casirivimab = ifelse(is.na(Casirivimab), "<8", Casirivimab),
         Casirivimab_perc = ifelse(Casirivimab_perc == "NA (NA-NA)", "--", Casirivimab_perc))

write_csv(table_elig_treat_redacted, fs::path(output_dir_rmd, "table_1.csv"))

colnames(table_elig_treat_redacted) <- c("STP Decile", "Count", "Count", "%", "Count", "%", 
                                         "Count", "%", "Count", "%", "Count", "%", 
                                         "Count", "%")
table_elig_treat_redacted %>%
  kable(row.names = FALSE, 
        align = c("l", rep("c", 13)),
        booktabs=TRUE) %>%
  kable_styling(position = "center", full_width = T, bootstrap_options = "striped", font_size = 10)  %>%
  #row_spec(1, bold = T) %>%
  column_spec(1, bold = T, width = "10em") %>%
  column_spec(2, width = "5em") %>%
  column_spec(4, background = "lightgrey")  %>%
  add_header_above(., c(" ", "Eligible", "All" = 2, "Paxlovid" = 2, "Sotrovimab" = 2, "Remdesivir" = 2,
                        "Molnupiravir" = 2, "Casirivimab" = 2)) %>%
  add_header_above(., c(" ", "", "Treated" = 12)) %>%
  add_footnote(c("All percentages (%) are caluclated with 95% confidence intervals"), 
               notation = "symbol")

```
